\documentclass{article}
\usepackage[active,tightpage]{preview}
\renewcommand{\PreviewBorder}{0.5in}
\usepackage[landscape]{geometry}
\usepackage{hyperref, multicol, fontspec}
\hypersetup{extension = }
\setmainfont{Nexus Sans Pro}
\frenchspacing
\begin{document}
\begin{preview}
\noindent \textsc{\Huge Tyler Nguyen} {\large\quad \href{about.pdf}{about} \ \href{resume.pdf}{\textbf{\textbullet r\'esum\'e}} \ \href{contact.pdf}{contact}}

\noindent\dotfill
\subsection*{Education}
\textbf{University of California, Berkeley} \hfill \textit{2014--2018}\\
B.S. Electrical Engineering and Computer Sciences (CSE) \hfill \textit{GPA: 3.537}
\begin{multicols}{2}
\begin{itemize}
\item CS 61A: Structure and Interpretation of Computer Programs
\item CS 61B: Data Structures and Advanced Programming
\item CS 61C: Machine Structures
\item Physics 7B: Heat, Electricity, and Magnetism
\item Math 54: Linear Algebra and Differential Equations
\item EE 16A/B: Designing Information Devices and Systems
\item CS 70: Discrete Mathematics and Probability Theory
\item CS 170: Efficient Algorithms and Intractable Problems
\item CS 188: Introduction to Artificial Intelligence
\item CS 189: Introduction to Machine Learning
\item EE 127: Optimization Models and Applications
\item CS 162: Operating Systems and Systems Programming
\item CS 168: Introduction to the Internet
\item CS 161: Computer Security
\item Statistics 155: Game Theory
\end{itemize}
\end{multicols}
\subsection*{Experience}
\begin{itemize}
\item \textbf{Software Engineer} at Google \hfill \textit{June 2018--present}\\
As a developer for Cloud Apigee Integration, I implemented core backend functionality, improved test quality and coverage, and led the initiative to integrate with a platform providing numerous connectors between first- and third-party services.
\item \textbf{Software Engineering Intern} at Cisco Systems \hfill \textit{May--August 2017}\\
On an identity management project, I helped complete the frontend for tenancy administration and integrated it with the backend server.  In addition, I created a configurable logging and capping system for email and SMS notifications, accessible via a REST API.
\item \textbf{Developer} at Medium One \hfill \textit{May--August 2016}\\
Medium One is a platform for gathering and processing data from IoT devices.  I contributed to a Wi-Fi module driver for a microcontroller along with the software that allowed it to securely access the platform.  I also created a preliminary implementation of a connector between the platform and a third-party service and created workflows to process sensor data.
\end{itemize}
\subsection*{Skills}
\begin{multicols}{2}
\subsubsection*{Programming Languages}
\begin{itemize}
\item Proficient in: Python, Java, C
\item Experience with: Bash, Scheme, MIPS ASM, React.js
\end{itemize}
\subsubsection*{Other Software}
\begin{itemize}
\item Microsoft Office (Word, PowerPoint, Excel)
\item Adobe CS6 (Photoshop, Illustrator, InDesign)
\item Git version control system
\item Docker/Kubernetes containerization system
\item \LaTeX \ typesetting system
\item REAPER Digital Audio Workstation
\end{itemize}
\subsubsection*{Notable Projects}
\begin{itemize}
\item \textbf{Scheme} (Python)\\
Developed a Scheme interpreter to demonstrate understanding of recursion, scoping, and parsing.
\item \textbf{Gitlet} (Java)\\
Designed and implemented a simplified version of the Git version control system based on serialization.
\item \textbf{Horse} (Python)\\
Leveraged randomized graph traversals with a heuristic, dynamic programming, and post-processing to approximate solutions to an NP-hard problem.
\item \textbf{Pintos Operating System} (C)\\
Implemented multiple process schedulers (priority donation, MLFQS), system calls for loading user programs, and a filesystem with directories.
\end{itemize}
\end{multicols}
\end{preview}
\end{document}
